A Survey of Quantitative Descriptions of Molecular Structure

### 2012-03-20 paper.tex
Added some more text

Topological descriptors take into account connectivity along with atom
and bond labels. These descriptors essentially consider the molecule
as a labeled graph and characterize it using graph invariants. In
addition to graph invariants, topological descriptors based on
information theory such as entropy \cite{Dehmer:2009uq}. An advantage
of these descriptors is that do not require any intensive
pre-processing steps such as 3D coordinate generation and
conformational analysis. In addition, many graph invariants can be
rapidly computed for graphs corresponding to small molecule structures
(even though they may be computationally intractable on much larger
graphs). While this class of descriptors have been used extensively in
predictive modeling applications [REFS], a key drawback is their lack
of interpretability. Given the abstract nature of the many graph
invariants and information theoretic descriptors, their use in
predictive models makes it difficult to explain the model in simple
physicochemical terms.

@@

>>>>

Topological descriptors take into account connectivity along with atom
and bond labels. These descriptors essentially consider the molecule
as a labeled graph and characterize it using graph invariants. In
addition to graph invariants, topological descriptors based on
information theory such as entropy \cite{Dehmer:2009uq}. An advantage
of these descriptors is that do not require any intensive
pre-processing steps such as 3D coordinate generation and
conformational analysis. In addition, many graph invariants can be
rapidly computed for graphs corresponding to small molecule structures
(even though they may be computationally intractable on much larger
graphs). While this class of descriptors have been used extensively in
predictive modeling applications [REFS], a key drawback is their lack
of interpretability. Given the abstract nature of many graph
invariants and information theoretic descriptors, their use in
predictive models makes it difficult to explain the model in simple
physicochemical terms.

@@

While library calls for descriptor evaluation is the most flexible
approach, it is not useful for non-programmers as well as users who
simply need a descriptor matrix for modeling or searching. As a
result, GUI or command line wrappers around descriptor APIs enable
easier usage. The CDKDescUI
application(\url{http://rguha.net/code/java/cdkdesc.html}) is a Java
Swing application that exposes the CDK descriptor and fingerprint
API's. It allows the users to specify a SMILES or SD file and evaluate
a selected set of descriptors or fingerprints and export them to a
text file. The application also has a command line mode that can be
run in server environments. A similar application is PaDEL
(\url{http://padel.nus.edu.sg/software/padeldescriptor/}) that
includes the CDK descriptors and also implements a number of
additional descriptors [SOME MENTION OF THESE?]

In addition to libraries and their wrappers there are various GUI
applications that allow easy descriptor calculations. Examples include
Bioclipse \cite{Spjuth:2007aa}, MOE (Chemical Computing Group) and
Maestro (Schr\"{o}dinger, Inc.)

\subsection{Comparing implementations}
\label{sec:comp-impl}
